Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
rewrite deriv of regular

\section{\our for continual learning}
\label{app:cl}
This section provides additional details about the derivation of the \our-based regularizer described in \cref{sec:sequential} and how we extended it for dealing with the multi-output setting in our experiments.
\subsection{Derivation of the regularizer term}
For continual learning, the model cannot access the training data from previous tasks up to task $t-1$, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task $t$ receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$. On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
\begin{equation}
	\weights^* = \arg \min_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \arg \min_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
\end{equation} 
Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$. As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}. Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
%
\begin{align} \label{eq:normal}
	q(\vu)
	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
        & \propto p(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu),
\end{align}
% The first normals are the approximate likelihoods 
where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the inducing points $p(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from the sparse approximation to the likelihood. Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel is the linear kernel. We therefore use the key quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer as the missing data term, which after we take the $\log$ becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.  Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.

>>>>

\subsection{Computational complexity}

\section{\our for continual learning}
\label{app:cl}
This section provides additional details about the derivation of the \our-based regularizer described in \cref{sec:sequential} and how we extended it for dealing with the multi-output setting in our experiments.
\subsection{Derivation of the regularizer term}
For continual learning, the model cannot access the training data from previous tasks up to task $t-1$, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task $t$ receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$. On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
\begin{equation}
	\weights^* = \arg \min_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \arg \min_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
\end{equation} 
Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come from $f^{\textrm{old}}_\weights(\vz_i) \sim q^\textrm{old}(\vu),  \forall \vz_i \in \mathcal{Z}_t$. As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp} as linked to approximate likelihood terms. Using this insight, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
%
\begin{align} \label{eq:normal}
	q(\vu)
	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
        & \propto p(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu),
\end{align}
% The first normals are the approximate likelihoods 
where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the inducing points $p(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from the sparse approximation to the likelihood. Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel is the linear kernel. We therefore use the key quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer as the missing data term, which after we take the $\log$ becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.  Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
